---
title: "Week7_R_demo"
author: 'Instructor: Jie Wang'
date: "3/05/2024"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Sample Mean, Sample Median

This is a demo corresponding to page 8, 9, 10
```{r Mean_Median}
data <- c(12.6, 12.9, 13.4, 12.3, 13.6, 13.5, 12.6, 13.1)

print(mean(data))

print(median(data))

data_table <- table(data)
max_freq <- max(data_table)
mode <- names(data_table)[data_table == max_freq]
print(mode)
```


#### Sample Range, Sample Variance, and Sample IQR
This is a demo corresponding to page 18
```{r range_variance_IQR}
data <- c(3,1,1,0,5,4,13,3)
#data <- c(74.001, 74.003, 74.015, 74.000, 74.005, 74.002, 74.005, 74.004)
print(max(data) - min(data))

print(var(data))

data_quantiles <- quantile(data, probs = c(0.25, 0.75))
print(data_quantiles)
print(data_quantiles[2] - data_quantiles[1])
```


#### Covariance and Correlation
This is a demo corresponding to page 23
```{r cov_cor}
x <- c(1.0840, 1.9112, 3.0100, 3.9455, 5.0304, 5.9400, 7.0490, 8.0739, 9.1712, 9.9806)
y <- c(1.7862, 2.1160, 2.5355, 2.4928, 2.8961, 3.0124, 3.3437, 3.2039, 3.5802, 3.6792)
plot(x, y, main = "Scatter Plot", xlab = "gas price", ylab = "expenditure", col = "blue", pch = 19)
print(cov(x,y))
print(cor(x,y))
```

#### Pie Chart
This is a demo corresponding to page 28
```{r pie_chart}
labels <-c("Ginger", "Saffron", "Cumin")
values <- c(0.32, 0.43, 0.25)
pie(values, labels = labels, main = "Pie Chart", col = rainbow(length(labels)))
legend("topright", labels, cex = 0.8, fill = rainbow(length(labels)))
```



#### Stem and Leaf Diagram

This is a demo corresponding to page 30
```{r Stem_leaf}
x <- c(33, 28, 16, 35, 11, 44, 33, 38)
stem(x, scale=1, width=100)
```


#### Histogram

This is a demo corresponding to page 37
```{r Histogram}
data <- c(9,5,1,4,4,7,2,5,3,8,7,6,5,8,2)
hist(data, breaks = 9)
```

#### Pareto chart

This is a demo corresponding to page 41
```{r pareto_chart}
#install.packages("qcc")
library(qcc)

counts <- c(60, 50, 40, 30, 20, 10)
names(counts) <-  c("Traffic", "Child Care", "Public Transportation", "Weather", "Overslept", "Emergency")
# Create Pareto chart
pareto.chart(counts, main = "Pareto Chart", ylab = "Frequency", col = "skyblue", bar.col = "lightblue")

```


#### Bar chart
This is a demo corresponding to page 42
```{r bar_chart}
categories <- c("A", "B", "C", "D")
values <- c(20, 30, 25, 35)

# Create bar chart
barplot(values, names.arg = categories, main = "Bar Chart", xlab = "Categories", ylab = "Values", col = "skyblue", horiz=TRUE)
barplot(values, names.arg = categories, main = "Bar Chart", xlab = "Categories", ylab = "Values", col = "skyblue", horiz=FALSE)

```


#### Bar chart
This is a demo corresponding to page 44


```{r box_plot}
data1 <- c(5, 10, 15, 20, 25)
data2 <- c(30, 35, 40, 45, 50)
data3 <- c(55, 60, 65, 70, 75)

# Combine the datasets into a list
all_data <- list(data1, data2, data3)

print(all_data)
# Create box plot
boxplot(all_data, main = "Box Plot of Three Datasets", ylab = "Values", col = c("skyblue", "lightgreen", "lightpink"))

```

#### Time Series Plot
This is a demo corresponding to page 46

```{r time_plot}
seq <- seq(from = 1, to = 100, by = 1) + 10 
y <- seq + rnorm(100, sd = 5) 
timeseries <- ts(y, start=c(2000, 1), frequency = 4) 
print(timeseries)
plot(timeseries)
```










