---
title: '0416'
author: "Jie Wang"
date: "4/18/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Demo Code for Slide Page 7
```{r demo_1}
data1 <- read.table("Example_1.txt")
x <- data1$V1
y <- data1$V2
model <- lm(y~x)
summary(model)
```
Based on the result above, we build the regression model $\hat{y}=74.283 + 14.947x$.

#### Demo Code for Slide Page 10 
We build $\hat{\beta}_0$ and $\hat{\beta}_1$ using the provied statistics. Recall
$$\hat{\beta}_1=\frac{S_{xy}}{S_{xx}}$$ and $\hat{\beta}_0=\bar{y} - \hat{\beta}_1\bar{x}$. Moreover,
$$
S_{xx}=\sum_{i}x_i^2 - \frac{1}{n}(\sum_{i}x_i)^2,\qquad
S_{xy}=\sum_ix_iy_i - \frac{1}{n}(\sum_ix_i)(\sum_iy_i).
$$
```{r demo_2}
sum_x_i  = 6322.28
sum_x2_i = 162674.18
sum_y_i  = 4757.90
sum_y2_i = 107679.27
sum_xy_i = 125471.10
n        = 250

Sxy <- sum_xy_i - 1/n * sum_x_i * sum_y_i
Sxx <- sum_x2_i - 1/n * (sum_x_i^2)
beta1 <- Sxy / Sxx
beta0 <- sum_y_i/n - beta1 * sum_x_i/n
print(c(beta0, beta1))
```
Based on the result above, we find $\hat{\beta}_0=-27.642$ and $\hat{\beta}_1=1.846$

#### Demo Code for Slide Page 14
```{r demo_3}
data1 <- read.table("house.txt",header=FALSE)
y <- data1$V1
x <- data1$V2
model <- lm(y~x)
summary(model)

plot(x,y,xlab="Tax",ylab="Price")
abline(13.3202,3.3244)
```



#### Demo Code for Slide Page 20

```{r demo_4}
data1 <- read.table("house.txt",header=FALSE)
y <- data1$V1
x <- data1$V2
model <- lm(y~x)
residual = resid(model)

plot(x,residual,xlab="Tax",ylab="Residual")
abline(0,0)
```



#### Demo Code for Slide Page 31, 33

```{r demo_5}
data <- read.table("Example_1.txt")
x <- data[,1]
y <- data[,2]
model <- lm(y~x)
predict(model, data.frame(x = 1), interval=c("prediction"))

```



#### Demo Code for Slide Page 45

```{r demo_6}
x <- c(215, 201, 196, 226, 226, 348, 226, 348, 148)
y <- c(30.8, 32.5, 35.4, 28.1, 24.4, 24.4, 28.5, 24.2, 32.8)
model <- lm(y~x)
summary(model)
```







